A Generic and Efficient E-field Parallel Imaging Correlator for Next-Generation Radio Telescopes

### 2015-11-06 imaging_demo/ms.tex
Update section 1 with changes suggested by Adam
From a01e819 (master):
=====================

In ms.tex,

(*) Update section 1 with changes suggested by Adam

We begin with a technical description of the algorithm in \S\ref{sec:math}, 
then discuss our particular implementation in \S\ref{sec:software}. We then 
verify the output data quality from our code in \S\ref{sec:verify} by presenting 
simulated images from both the EPIC correlator and comparing to a simulated FX 
correlator. We also demonstrate the performance with real-world data from the 
LWA. In \S \ref{sec:analysis}, we explore the scalability of the algorithm in the 
context of several array design choices. We identify specific array design 
classes where the EPIC correlator -- is computationally more efficient; and in 
the field of transients, demands significantly lesser I/O bandwidth relative to 
visibility based approaches. We conclude and discuss future research prospects 
in \S\ref{sec:conclusions}.

>>>>

We begin with a technical description of the algorithm in \S\ref{sec:math}, 
then discuss our particular implementation in \S\ref{sec:software}. We then 
verify the output data quality from our code in \S\ref{sec:verify} by presenting 
simulated images from both the EPIC correlator and comparing to a simulated FX 
correlator. We also demonstrate the performance with real-world data from the 
LWA. In \S \ref{sec:analysis}, we explore the scalability of the algorithm in the 
context of several array design choices. We identify specific array design 
classes where the EPIC correlator is computationally more efficient and in the 
field of transients, demands significantly lesser I/O bandwidth relative to 
visibility based approaches. We conclude and discuss future research prospects 
in \S\ref{sec:conclusions}.
